notes

### 2025-07-09 manuscript/notes/notes.Rmd
update Notes and ResponseToReviewers
add reference to Frank et al., 2025
more notes on the revision

@@

And in the response to the reviewer, let's NOT say "We have no idea why the models did not converge ..."
Instead, let's say it is common for models to fail to converge in lme4 when they have a reasonably complex random effects structure. (We can also say this in the tutorial or supps, as necessary).
And then can we cite the lme4 tutorial paper or something else to provide a resource for folks to use?

@@

@@

@@

@@

>>>>

-> corrected.

@@

And in the response to the reviewer, let's NOT say "We have no idea why the models did not converge ..."
Instead, let's say it is common for models to fail to converge in lme4 when they have a reasonably complex random effects structure. (We can also say this in the tutorial or supps, as necessary).

And then can we cite the lme4 tutorial paper or something else to provide a resource for folks to use?

@@

-> I added a reference.

@@

-> No we did not. I changed this to make a distinction between model prediction (for the model comparison section) and model inference.

@@

-> I added this reference to the ms.

@@

# July 9th #

- figure 1 legend.

write out EHA/SAT in full. At this stage, these terms have not been defined, so using abbreviations is meaningless. Or just remove the labels completely and say " ... versus a distributional analysis".

the brackets are wrong in the Figure 1 legend. (0,100]. This should be [0,100], right? This happens twice.

- page 6. first para. EHA is not defined in the main text yet, but we use the abbreviation. We cannot do this. And int he response, don't we say that we are not doing this? This becomes very confusing and incoherent. We have to define any abbreviations we use at their first instance in the main text.

One option would be to add a line on page 3 para 2, like this:

...compared to the aggregation of data across trials (Figure 1A), a distributional approach known as event history analysis (EHA) offers ...

If not here, we need it somewhere else. This is really basic and needs to done consistently.

- page 13. tutorials. I would get rid of all of the package references to ease the flow of reading. Can they go in supplementary materials? Or somewhere else? At the moment, it isn't working with them piled into a massive paragraph.

- page 19. delete the sentence below, as we already say that earlier in the manuscript:

>Too small bin widths...

- Figure 3. Can you make the figure longer? It looks squashed and is hard to see/understand. If it takes up the whole page and the legend goes off the page, then that's ok. Same goes for Figure 4 also.

- Figures 3 and 4. The colours are wrong in panel C. This is really confusing. We need to set the colours to be consistent. e.g., if congruent is orange on A and B, it should be orange in C. To do so, in the code for panel C, you need to use scale_fill_manual(values=c("#D95F02FF", "#7570B3FF")). ANd then choose the relevant hex codes e.g., https://emilhvitfeldt.github.io/r-color-palettes/discrete/RColorBrewer/Dark2/index.html.

Does this make sense? It is really important. Please check the colour codes are correct.

- page 33. para 2. We need to cite Bates et al., 2015 for the lme4 package.

- in the manuscript.Rmd file, can we delete all text that we are not keeping? It seems really untidy/annoying to have loads of text commented out. Does this make sense? Just delete it and commit the change. I already deleted some stuff, but there is more to do maybe?
